Turbulence and Particle Acceleration in Giant Radio Haloes: the Origin of Seed Electrons

### 2016-09-06 paper.tex
added clarification to the caption of Fig 7

\begin{figure*}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio profiles}\\
     \includegraphics[width=\columnwidth]{figure7_prof.eps}
   \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio spectra}\\
     \includegraphics[width=\columnwidth]{figure7_spec.eps}
   \end{center}
\end{minipage}
\caption{\C{Sensitivity of radio emission in the Coma cluster to critical
    parameters when we vary the ratio of the time scales on which turbulence is
    active ($\tau_{\rm cl}$) to the turbulent re-acceleration time ($\tau_{\rm
      D}$). In comparison to Figure~\ref{fig:param_comp}, we change our fiducial
    model (solid lines) and adopt a slightly more extended spatial distribution
    of CRs ($\alpha_{\rm CR, spat}=0.5$) and lower the CR-to-thermal energy by a
    factor of five; otherwise, we adopt $X_\rmn{tu}=0.2$, $\alpha_\rmn{tu}=0.8$,
    $\tau_{\rm cl}=2.5\,\tau_{\rm D}$ as fiducial values and vary each parameter
    separately in each row of panels. Radio surface brightness profiles (left)
    are contrasted to radio synchrotron spectra (right; for more details see
    caption to Figure~\ref{fig:param_comp}).  Provided there is a minimum
    (threshold) level of turbulence ($X_\rmn{tu}\gtrsim0.2$), here the radio
    profiles are mainly determined by the CR distribution, while turbulence
    has a smaller impact. In the bottom two panels we vary the exponential
    momentum growth factor $\tau_{\rm cl}/\tau_{\rm D}$ (see
    equations~\ref{eq:pexp} and \ref{eq:Creacc}), which mainly changes the
    normalisation of the CR distribution and neither spectral shape nor radial
    synchrotron profile. Interestingly, the flat CR profiles adopted here are
    similar to those required to reproduce the radio profiles in our CR
    streaming model (see Figure~\ref{fig:sync_profile}).}}
  \label{fig:param_comp_tcl_tD}
\end{figure*}

>>>>

\begin{figure*}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio profiles}\\
     \includegraphics[width=\columnwidth]{figure7_prof.eps}
   \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio spectra}\\
     \includegraphics[width=\columnwidth]{figure7_spec.eps}
   \end{center}
\end{minipage}
\caption{\C{Sensitivity of radio emission in the Coma cluster to critical
    parameters when we vary the ratio of the time scales on which turbulence is
    active ($\tau_{\rm cl}$) to the turbulent re-acceleration time ($\tau_{\rm
      D}$). In comparison to Figure~\ref{fig:param_comp}, we change our fiducial
    model (solid lines) and adopt a slightly more extended spatial distribution
    of CRs ($\alpha_{\rm CR, spat}=0.5$) and lower the CR-to-thermal energy by a
    factor of five; otherwise, we adopt $X_\rmn{tu}=0.2$, $\alpha_\rmn{tu}=0.8$,
    $\tau_{\rm cl}=2.5\,\tau_{\rm D}$ as fiducial values and vary each parameter
    separately in each row of panels. Radio surface brightness profiles (left)
    are contrasted to radio synchrotron spectra (right; for more details see
    caption to Figure~\ref{fig:param_comp}). Provided there is a minimum
    (threshold) level of turbulence ($X_\rmn{tu}\gtrsim0.2$), here the radio
    profiles are mainly determined by the CR distribution, while turbulence has
    a smaller impact. In the bottom two panels we vary the exponential momentum
    growth factor $\tau_{\rm cl}/\tau_{\rm D}$ (see equations~\ref{eq:pexp} and
    \ref{eq:Creacc}), but unlike $X_\rmn{tu}$ should not vary strongly with
    time. Instead, it mainly changes the normalisation of the CR distribution
    and neither spectral shape nor radial synchrotron profile. Interestingly,
    the flat CR profiles adopted here are similar to those required to reproduce
    the radio profiles in our CR streaming model (see
    Figure~\ref{fig:sync_profile}).}}
  \label{fig:param_comp_tcl_tD}
\end{figure*}
